PropOcData2

### 2021-08-22 R/PropOc Data 3D.Rmd

PlotPropOcAllMeanSD <- function(relation) {
  plot1<- ggplot()+
    geom_linerange(data=combinedData %>% filter(Relation ==relation), 
                   aes(x=Distance,ymax=MeanPropOcc+SDPropOcc,ymin=MeanPropOcc-SDPropOcc, color = Strain, linetype =factor(BioRep), group = Experiment),
                   position = position_dodge(width =.8), size=.7)+
    facet_wrap(~Time, ncol = 3)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title =paste0(relation, " proportional occupancy mean +/- SD"), linetype = "Biological Replicate")+
    theme_minimal_grid()+
    background_grid()+
    theme(plot.title = element_text(hjust = 0.5))
  ggsave(paste0(relation,".png"),plot = plot1, width = 20, height = 10)
}
PlotPropOcAllMeanSD("Pa->Pa")
PlotPropOcAllMeanSD("Pa->Sa")
PlotPropOcAllMeanSD("Sa->Sa")
PlotPropOcAllMeanSD("Sa->Pa")
```
Another metric used is the coefficient of variation, CV, which is the ratio of the standard deviation to the mean.So, let's also visualize that.
```{r Plot CV} 
PlotCVrelation <- function(relation){
  plot1<-ggplot()+ 
    geom_point(data=combinedData %>% filter(Relation =="Pa->Pa"), 
               aes(x=Distance,y = CV, color = Strain, shape = factor(BioRep), group = Experiment),
               position = position_dodge(width =.8), size=4)+
    geom_hline(yintercept = 1, linetype = "dashed")+
    facet_wrap( ~ Time, ncol = 3)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title =paste0(relation, " proportional occupancy Coefficient of variation (SD/mean)"), linetype = "Biological Replicate")+
    theme_minimal_grid()+
    background_grid()+ 
    theme(plot.title = element_text(hjust = 0.5)) 
  ggsave(paste0(relation,"-CV.eps"),plot = plot1, width = 20, height = 10)
  ggsave(paste0(relation,"-CV.png"),plot = plot1, width = 20, height = 10)
  }
PlotCVrelation("Pa->Pa")
PlotCVrelation("Pa->Sa")
PlotCVrelation("Sa->Sa")
PlotCVrelation("Sa->Pa")
```
# Importing whole data sets to identify distribution of data
```{r read whole data sets}

ReadPropOcFile<-function(file){
    propOcData<-read.csv(file,header = T)
    fileName<-str_split(basename(file), "\\.")[[1]][1]#this selects the base file name and removes the ".csv"
    print(paste0("Importing sample ", fileName))
    attrList<-str_split(fileName,"_")[[1]]
    propOcData<-propOcData %>% mutate(Condition = attrList[1], TimePoint = attrList[2], Replicate = attrList[3], SampleCode = fileName)
    return(propOcData)
    }

@@

GetHistograms<-function(inputData){
data<-inputData%>% group_by(SampleCode,Distance, source) 
  dataList<-group_split(data)#split data fram into a list of dataframes with a single distance and from a single source
  histogramList<-map(dataList, HistogramDistance)#run the function on each item of the list created at the top
  output<-bind_rows(histogramList) #go back to a single dataframe 
  return(output)
}
HistogramDistance <- function(df) {
  #histogram<- hist(df$PropOc) 
  histogram<- hist(df$PropOc1, breaks = seq.int(0,1,.01)) 
  #histogram<- hist(df$PropOc, breaks = c(0,lseq(.001,1.03,100)))
  #histogram<- hist(df$PropOc, breaks = c(0,lseq(.0001,1.03,100)))
  output<-data.frame(histogram$mids,histogram$counts, histogram$density)
  colnames(output)<-c("Value", "Frequency", "Density")
  output<-output %>% mutate(Distance = df$Distance[[1]]) %>% filter(!Frequency==0)
  output<-output %>% mutate(Source = df$source[[1]])
  output<-output %>% mutate(Sample = df$SampleCode[[1]])
  return(output)
}
#Run histograms for data
propOcHistogramData<-GetHistograms(PropOcDataFiltered)#from here what matters is the density since it is freq/total*#ofbins
propOcHistogramData<-propOcHistogramData %>% group_by(Sample, Source, Distance) %>% mutate(count = sum(Frequency), NormDensity = Density/100) %>% ungroup()

#plot distributions
PlotAllPropOcData <- function(sample ) {
  ggplot()+ 
    geom_point(data = propOcHistogramData %>% filter(Sample ==sample),aes(x=Value,y=NormDensity, color = Distance),size=2)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    scale_color_gradientn(colours = rainbow(5))+
    facet_wrap(.~Source)+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}
PlotAllPropOcData("wt_d1_05")#looks cool, so let's keep going...

#now calculate the maximum frequency
propOcMaxDensity<-propOcHistogramData %>% 
    group_by(Sample, Distance, Source)%>% 
    mutate(MaxDensity = max(NormDensity)) %>% 
    mutate(DensityCh = ifelse(Density ==max(Density), 1, 0 )) %>% filter(DensityCh==1) %>% ungroup()#find max density, check where it matches
  propOcMaxDensityDoubles<-propOcMaxDensity %>% group_by(Sample,Distance, Source) %>% mutate(DoubledValues = sum(DensityCh)) %>% filter (DoubledValues>1)#this is just to find which values were repeated

  PlotMaxDensities <- function(sample) {
  ggplot()+
    geom_jitter(data = propOcMaxDensity %>% filter(Sample ==sample),aes(x=Value, y=Density,color = Distance),size=2)+
    labs(title ="Maximum Density")+
    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    facet_wrap( ~ Source, ncol = 2)+
    scale_color_gradientn(colours = rainbow(5))+
    #scale_shape_manual(values=c(0,1,2, 15,16,17))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}
PlotMaxDensities("wt_d1_05")
  #maximum distribution isn't super representative, so for the distribution, I calculated the value at which 50% of the population is found

#Median distribution
getDeathCurve<-function(df){
  currentDensity = 0
  for (i in 1 : nrow(df)){
    addeddensity<-1-currentDensity
    df[i,9]<-addeddensity
    df[i,10]<-currentDensity
    currentDensity = currentDensity+df[i,8]
  }
  colnames(df)<-c("Value","Frequency","Density", "Distance", "Source","Sample", "count", "NormDensity", "Decay", "currentDens")
  df<-df %>% mutate (normDecay = (Decay - min(Decay)) / (max(Decay) - min(Decay)), DeltaDens = abs(Decay-currentDens))
  return(df)
  }
GetPercentiles<-function(input){
  df<-input %>% group_by(Sample, Distance, Source)
  yas<- group_split(df)
  mappedData<-map(yas, getDeathCurve)
  boundData<-bind_rows(mappedData)
return(boundData)}

@@

PlotPercentiles <- function(df) {
  ggplot()+
    geom_point(data = df,aes(y=Value, color=normDecay,x = Distance, shape = Sample),size=2)+
    #geom_pointrange(data = df,aes(x = Distance,y=meanValue,ymax=meanValue+SdValue,ymin=meanValue-SdValue, color=Strain),size=2)+
    labs(title ="50 percentile Density")+
    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    facet_wrap( ~ Source, ncol = 2)+
    scale_color_gradientn(colours = rainbow(5))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
  }
PlotPercentiles(test50Percentile)#test case for sample wt_d1_05

@@

ggplot()+#linear
    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Pa"),aes(y=meanValue, x = Distance,color=Condition, shape = "Mean"),size=2)+
    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Pa"),aes(y=medianValue, x = Distance,color=Condition,shape = "Median"),size=2)+
    labs(title ="mean 50 percentile Density")+
    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    facet_grid(Relation ~ TimePoint)+
    #scale_color_gradientn(colours = rainbow(5))+
    #scale_shape_manual(values=c(0,1,2, 15,16,17))+
    scale_color_brewer(palette = "Set1")+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))

ggplot()+#linear
    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Sa->Sa"),aes(y=meanValue, x = Distance,color=Culture, shape = "Mean"),size=2)+
    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Sa->Sa"),aes(y=medianValue, x = Distance,color=Culture,shape = "Median"),size=2)+
    labs(title ="mean 50 percentile Density")+
    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    facet_grid(Strain ~ TimePoint)+
    #scale_color_gradientn(colours = rainbow(5))+
    #scale_shape_manual(values=c(0,1,2, 15,16,17))+
    scale_color_brewer(palette = "Set1")+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))

@@

PlotEnrichment <- function(df) {
ggplot()+#first run
    geom_point(data = df,aes(y=Distance, x = Sample, color = Enrichment, shape = Sample),size=2)+
    labs(title ="50 percentile Enrichment")+
    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    facet_wrap( ~ Source, ncol = 2)+
    scale_color_gradientn(colours = rainbow(5))+
    scale_shape_manual(values=c(0,1,2, 15,16,17))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}

>>>>

PlotPropOcAllMeanSD <- function(relation) {
  plot1<- ggplot()+
    geom_linerange(data=combinedData %>% filter(Relation ==relation), 
                   aes(x=Distance,ymax=MeanPropOcc+SDPropOcc,ymin=MeanPropOcc-SDPropOcc, color = Strain, linetype =factor(BioRep), group = Experiment),
                   position = position_dodge(width =.8), size=.7)+
    facet_wrap(~Time, ncol = 3)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title =paste0(relation, " proportional occupancy mean +/- SD"), linetype = "Biological Replicate")+
    theme_minimal_grid()+
    background_grid()+
    theme(plot.title = element_text(hjust = 0.5))
  ggsave(paste0(relation,".png"),plot = plot1, width = 20, height = 10)
}
PlotPropOcAllMeanSD("Pa->Pa")
PlotPropOcAllMeanSD("Pa->Sa")
PlotPropOcAllMeanSD("Sa->Sa")
PlotPropOcAllMeanSD("Sa->Pa")
```
Another metric used is the coefficient of variation, CV, which is the ratio of the standard deviation to the mean.So, let's also visualize that.
```{r Plot CV} 
PlotCVrelation <- function(relation){
  plot1<-ggplot()+ 
    geom_point(data=combinedData %>% filter(Relation =="Pa->Pa"), 
               aes(x=Distance,y = CV, color = Strain, shape = factor(BioRep), group = Experiment),
               position = position_dodge(width =.8), size=4)+
    geom_hline(yintercept = 1, linetype = "dashed")+
    facet_wrap( ~ Time, ncol = 3)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title =paste0(relation, " proportional occupancy Coefficient of variation (SD/mean)"), linetype = "Biological Replicate")+
    theme_minimal_grid()+
    background_grid()+ 
    theme(plot.title = element_text(hjust = 0.5)) 
  ggsave(paste0(relation,"-CV.eps"),plot = plot1, width = 20, height = 10)
  ggsave(paste0(relation,"-CV.png"),plot = plot1, width = 20, height = 10)
  }
PlotCVrelation("Pa->Pa")
PlotCVrelation("Pa->Sa")
PlotCVrelation("Sa->Sa")
PlotCVrelation("Sa->Pa")
```
Importing whole data sets to identify distribution of data
the chunk below is the only one aplicable to the SaPa chronic wounds project, all the other ones are just for reference

```{r read whole data sets}
ReadPropOcFile<-function(file){
    propOcData<-read.csv(file,header = T)
    fileName<-str_split(basename(file), "\\.")[[1]][1]#this selects the base file name and removes the ".csv"
    print(paste0("Importing sample ", fileName))
    attrList<-str_split(fileName,"_")[[1]]
    propOcData<-propOcData %>% mutate(Condition = attrList[1], TimePoint = attrList[2], Replicate = attrList[3], SampleCode = fileName)
    return(propOcData)
    }

@@

#Functions to make histograms of proportional occupancy values
#####
GetHistograms<-function(inputData){
data<-inputData%>% group_by(SampleCode,Distance, source) 
  dataList<-group_split(data)#split data fram into a list of dataframes with a single distance and from a single source
  histogramList<-map(dataList, HistogramDistance)#run the function on each item of the list created at the top
  output<-bind_rows(histogramList) #go back to a single dataframe 
  return(output)
}
HistogramDistance <- function(df) {
  #histogram<- hist(df$PropOc) 
  histogram<- hist(df$PropOc1, breaks = seq.int(0,1,.01)) 
  #histogram<- hist(df$PropOc1, breaks = c(0,lseq(.001,1.03,100)))
  #histogram<- hist(df$PropOc1, breaks = c(0,lseq(.0001,1.03,100)))
  output<-data.frame(histogram$mids,histogram$counts, histogram$density)
  colnames(output)<-c("Value", "Frequency", "Density")
  output<-output %>% mutate(Distance = df$Distance[[1]]) %>% filter(!Frequency==0)
  output<-output %>% mutate(Source = df$source[[1]])
  output<-output %>% mutate(Sample = df$SampleCode[[1]])
  return(output)
}
#####
#Run histograms for data
propOcHistogramData<-GetHistograms(PropOcDataFiltered)#from here what matters is the density since it is freq/total*#ofbins
propOcHistogramData<-propOcHistogramData %>% group_by(Sample, Source, Distance) %>% mutate(count = sum(Frequency), NormDensity = Density/100) %>% ungroup()
#Some Quality control by removing samples with low counts:
#Quality control for low counts
lowcounts<-propOcHistogramData %>% filter(count<500)
lowcountssummary<-lowcounts %>% group_by(Sample, Source) %>% summarize(Lowcounts = n(), meanCounts = mean(count))

lowsamples<-unique(lowcounts$Sample)

ggplot()+
  geom_point(data = lowcounts,aes(x=Sample,y=count, color = Distance, shape = Source))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))

lowCountSamples<-bind_rows(propOcHistogramData %>% filter(Sample == "mono_d1_02"),
                           propOcHistogramData %>% filter(Sample == "phz_d4_08"),
                           propOcHistogramData %>% filter(Sample == "wt_d4_11") %>% filter(Source == "finalRG"))
propOcHistogramData <- anti_join(propOcHistogramData, lowCountSamples)

#plot distributions
PlotAllPropOcData <- function(sample ) {
  ggplot()+ 
    geom_point(data = propOcHistogramData %>% filter(Sample ==sample),aes(x=Value,y=NormDensity, color = Distance),size=2, shape = 1)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    scale_color_gradientn(colours = rainbow(5))+
    labs(title =sample)+
    facet_wrap(.~Source)+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}
PlotAllPropOcData("wt_d4_05")#looks cool, so let's keep going...

#now calculate the maximum frequency
#####
propOcMaxDensity<-propOcHistogramData %>% 
    group_by(Sample, Distance, Source)%>% 
    mutate(MaxDensity = max(NormDensity)) %>% 
    mutate(DensityCh = ifelse(Density ==max(Density), 1, 0 )) %>% filter(DensityCh==1) %>% ungroup()#find max density, check where it matches
  propOcMaxDensityDoubles<-propOcMaxDensity %>% group_by(Sample,Distance, Source) %>% mutate(DoubledValues = sum(DensityCh)) %>% filter (DoubledValues>1)#this is just to find which values were repeated

  PlotMaxDensities <- function(sample) {
  ggplot()+
    geom_jitter(data = propOcMaxDensity %>% filter(Sample ==sample),aes(x=Value, y=Density,color = Distance),size=2)+
    labs(title ="Maximum Density")+
    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    facet_wrap( ~ Source, ncol = 2)+
    scale_color_gradientn(colours = rainbow(5))+
    #scale_shape_manual(values=c(0,1,2, 15,16,17))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}
PlotMaxDensities("pqsL_d4_03")
#####
#maximum distribution isn't super representative, so for the distribution, I calculated the value at which 50% of the population is found

#Median distribution
#####
getDeathCurve<-function(df){
  currentDensity = 0
  for (i in 1 : nrow(df)){
    addeddensity<-1-currentDensity
    df[i,9]<-addeddensity
    df[i,10]<-currentDensity
    currentDensity = currentDensity+df[i,8]
  }
  colnames(df)<-c("Value","Frequency","Density", "Distance", "Source","Sample", "count", "NormDensity", "Decay", "currentDens")
  df<-df %>% mutate (normDecay = (Decay - min(Decay)) / (max(Decay) - min(Decay)), DeltaDens = abs(Decay-currentDens))
  return(df)
  }
GetPercentiles<-function(input){
  df<-input %>% group_by(Sample, Distance, Source)
  yas<- group_split(df)
  mappedData<-map(yas, getDeathCurve)
  boundData<-bind_rows(mappedData)
return(boundData)}

@@

PlotPercentiles <- function(df) {
  ggplot()+
    geom_point(data = df,aes(y=Value, color=normDecay,x = Distance, shape = Sample),size=2)+
    #geom_pointrange(data = df,aes(x = Distance,y=meanValue,ymax=meanValue+SdValue,ymin=meanValue-SdValue, color=Strain),size=2)+
    labs(title ="50 percentile Density")+
    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    facet_wrap( ~ Source, ncol = 2)+
    scale_color_gradientn(colours = rainbow(5))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
  }
PlotPercentiles(test50Percentile)#test case for sample wt_d1_05
PlotPercentiles(propOcMidDensity %>% filter(Sample == "wt_d4_05", Source == "finalGR"))

@@

ggplot()+
    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Sa"),aes(y=meanValue, x = Distance,color=Condition, shape = "Mean"),size=2)+
    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Sa"),aes(y=medianValue, x = Distance,color=Condition,shape = "Median"),size=2)+
    labs(title ="mean 50 percentile Density")+
    facet_grid(Relation ~ TimePoint)+
    scale_color_brewer(palette = "Set1")+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))

ggplot()+#Pa->Pa
    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Pa"),aes(y=meanValue, x = Distance,color=Culture, shape = "Mean"),size=2)+
    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Pa"),aes(y=medianValue, x = Distance,color=Culture,shape = "Median"),size=2)+
    labs(title ="mean 50 percentile Density")+
    facet_grid(Strain ~ TimePoint)+
    scale_color_brewer(palette = "Set1")+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))

#Calculate Enrichment
propOcEnrichment<- propOcMidDensitylabeled %>% group_by(SampleCode,Relation)%>%
  select(Value, Density, Distance, Relation,Sample, Strain,TimePoint, Condition, Culture, Strain,SampleCode) %>% mutate(Enrichment = max(Value)) %>%
  mutate(EnrichmentCh = ifelse(Enrichment == Value, 1, 0 )) %>% filter(EnrichmentCh==1) %>% 
  mutate(DoubledValues = sum(EnrichmentCh)) %>% ungroup()#find max
propOcEnrichment$SampleCode<-as.factor(propOcEnrichment$SampleCode)#make samples a factor

metaData.df <-read.csv('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/images metadata.csv', header = TRUE)
metaData.df$SampleCode<-as.factor(metaData.df$SampleCode)

metaData.df<-metaData.df %>% select(SampleCode, mouse, Position, size, Region, Zdim, xyDim,xySize)
pOEnrMeta<-metaData.df %>%  merge(propOcEnrichment, by = "SampleCode")

#Plotting Enrichment per Relation
PlotEnrichment<-function(relation){
  ggplot()+
    geom_point(data = pOEnrMeta %>% filter(Relation == relation),aes(y=Distance,x = Sample,shape = Region, color =Condition),size=2)+
    geom_point(data = pOEnrMeta %>% filter(Relation == relation),aes(y=WmeanDist, x = Sample, shape = Region), color ="BLACK",size=2)+
    labs(title =paste("50 percentile Enrichment", relation))+
    facet_grid(.~TimePoint,scales = "free", space = "free")+
    #scale_color_gradientn(colours = rainbow(5))+
    #scale_shape_manual(values=c(0,1,2, 15,16,17))+
    ylim(0,30)+
    theme_cowplot()+
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),plot.title = element_text(hjust = 0.5))+
    panel_border() 
}
PlotEnrichment("Pa->Sa")
PlotEnrichment("Sa->Pa")
PlotEnrichment("Sa->Sa")
PlotEnrichment("Pa->Pa")

#It's unclear how to deal with the issue of multiple enrichment distances, but I think doing a weighted mean makes the most sense:
pOEnrMetaClean<-pOEnrMeta %>% group_by(SampleCode,Condition,TimePoint, Region, Relation)%>%summarise(WmeanDist =weighted.mean(Distance, Density))
#now calculate the Mean per condition:
pOEnrMetaStatsRegion<-pOEnrMetaClean %>% group_by(Condition,TimePoint, Region, Relation) %>%
  summarise(meanED = mean(WmeanDist),medianED = median(WmeanDist), SDED = sd(WmeanDist), SEED = std.error(WmeanDist),per25 = quantile(WmeanDist, .25), per75 = quantile(WmeanDist, .75))

pOEnrMetaStats<-pOEnrMetaClean %>% group_by(Condition,TimePoint, Relation) %>%
  summarise(meanED = mean(WmeanDist),medianED = median(WmeanDist), SDED = sd(WmeanDist), SEED = std.error(WmeanDist), per25 = quantile(WmeanDist, .25), per75 = quantile(WmeanDist, .75))

#plot mean, weighted mean Enrichment distance from 50 percentile PO
##First using region
PlotMeanEnrichment50percent<-function(df1,df2){
  ggplot()+
    geom_pointrange(data = df1,aes(y=meanED,ymax=meanED+SEED,ymin=meanED-SEED, x = Condition,shape = Region),position = position_dodge(width = .5),size = .7)+
  geom_point(data = df2,aes(y=WmeanDist,x = Condition, group = Region),position = position_dodge(width = .5),size=1, shape = 1)+
    labs(y = expression(atop("Enrichment distance ("*mu*"m)",paste(italic("P. aeruginosa ") %->% italic("S. aureus"))))) +
    #facet_grid(.~Relation,scales = "free", space = "free")+
    theme_cowplot()+
    #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),plot.title = element_text(hjust = 0.5))+
    theme(plot.title = element_text(hjust = 0.5),
          strip.text = element_text(size = 12, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"))
}
PlotMeanEnrichment50percent(pOEnrMetaStatsRegion %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"),
                            pOEnrMetaClean %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"))

PlotMedianEnrichment50percent<-function(df1,df2){
  ggplot()+
    geom_pointrange(data = df1,aes(y=medianED,ymax=per25,ymin=per75, x = Condition,shape = Region),position = position_dodge(width = .5),size = .7)+
  geom_jitter(data = df2,aes(y=WmeanDist,x = Condition),width = .5, height = 0,size=1, shape = 1)+
    labs(y = expression(atop("Enrichment distance ("*mu*"m)",paste(italic("P. aeruginosa ") %->% italic("S. aureus"))))) +
    #facet_grid(.~Relation,scales = "free", space = "free")+
    theme_cowplot()+
    #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),plot.title = element_text(hjust = 0.5))+
    theme(plot.title = element_text(hjust = 0.5),
          strip.text = element_text(size = 12, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"))
}
PlotMedianEnrichment50percent(pOEnrMetaStatsRegion %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"),
                            pOEnrMetaClean %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"))
#then without region
PlotMedianEnrichment50percentNRegion<-function(df1,df2){
  ggplot()+
    geom_pointrange(data = df1,aes(y=medianED,ymax=per25,ymin=per75, x = Condition),size = .7)+
  geom_jitter(data = df2,aes(y=WmeanDist,x = Condition),width = .2, height = 0,size=1, shape = 1)+
    labs(y = expression(atop("Enrichment distance ("*mu*"m)",paste(italic("P. aeruginosa ") %->% italic("S. aureus"))))) +
    #facet_grid(.~Relation,scales = "free", space = "free")+
    theme_cowplot()+
    #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),plot.title = element_text(hjust = 0.5))+
    theme(plot.title = element_text(hjust = 0.5),
          strip.text = element_text(size = 12, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"))
}
PlotMeanEnrichment50percentNRegion<-function(df1,df2){
  ggplot()+
    geom_pointrange(data = df1,aes(y=meanED,ymax=meanED+SEED,ymin=meanED-SEED, x = Condition),size = .7)+
  geom_jitter(data = df2,aes(y=WmeanDist,x = Condition, group = Region),width = .2, height = 0,size=1, shape = 1)+
    labs(y = expression(atop("Enrichment distance ("*mu*"m)",paste(italic("P. aeruginosa ") %->% italic("S. aureus"))))) +
    #facet_grid(.~Relation,scales = "free", space = "free")+
    theme_cowplot()+
    #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),plot.title = element_text(hjust = 0.5))+
    theme(plot.title = element_text(hjust = 0.5),
          strip.text = element_text(size = 12, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"))
}
PlotMeanEnrichment50percentNRegion(pOEnrMetaStats %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"),
                            pOEnrMetaClean %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"))
PlotMedianEnrichment50percentNRegion(pOEnrMetaStats %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"),
                            pOEnrMetaClean %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"))

#original figure 
ggplot()+
    geom_pointrange(data = pOEnrMetaStats,aes(y=meanED,ymax=meanED+SEED,ymin=meanED-SEED, x = Condition),position = position_dodge(width = .5))+
  geom_jitter(data = pOEnrMetaClean,aes(y=WmeanDist,x = Condition),size=1, shape = 1, height = 0, width = .2)+
    labs(y = expression("Enrichment distance ("*mu*"m)")) +
    facet_grid(TimePoint~Relation,scales = "free", space = "free")+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5),
          strip.text = element_text(size = 12, margin = margin(.1,0,.1,0, "cm")),#this is for the facets
          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"))+
    panel_border()

ggplot()+
    geom_pointrange(data = pOEnrMetaStatsRegion,aes(y=meanED,ymax=meanED+SEED,ymin=meanED-SEED, shape = Region,x = Condition),
                    position = position_dodge(width = .5))+
    geom_point(data = pOEnrMetaClean,aes(y=WmeanDist,x = Condition, group = Region),position = position_dodge(width = .5),size=1, shape = 1)+
    labs(y = expression("Enrichment distance ("*mu*"m)")) +
    facet_grid(TimePoint~Relation,scales = "free", space = "free")+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5),
          strip.text = element_text(size = 12,margin = margin(.1,0,.1,0, "cm")),#this is for the facets
          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"))+
    panel_border()

@@

PlotEnrichment <- function(df) {
ggplot()+
    geom_point(data = df,aes(y=Distance, x = Sample, color = Enrichment, shape = Sample),size=2)+
    labs(title ="50 percentile Enrichment")+
    facet_wrap( ~ Source, ncol = 2)+
    scale_color_gradientn(colours = rainbow(5))+
    scale_shape_manual(values=c(0,1,2, 15,16,17))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}
